MCMC report

### 2020-06-18 doc/mcmc report/mcm-report.Rmd
map figure

---
title: "MCMC report"
author: "Eduardo Fernández Pascual"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output: pdf_document
---

@@

```{r message = FALSE, echo = FALSE, warning = FALSE}
library(tidyverse); library(here); library(readxl)

read_excel(here("results", "analysis", "results.preliminary.xlsx")) -> sheet1

sheet1[8:19, ]  %>%
  select(variable, post.mean, l.95..CI, u.95..CI, pMCMC) %>%
  separate(variable, into = c("Alpine", "Treatment"), sep = ":") %>%
  mutate(Alpine = gsub("Alpine", "", Alpine)) %>%
  rename(Mean = post.mean,
         Lower = l.95..CI,
         Upper = u.95..CI,
         p = pMCMC) -> df1

ggplot(df1, aes(y = Alpine, x = Mean, xmin = Lower, xmax = Upper, color = Alpine)) +
  geom_point() +
  labs(title = "Final germination proportion by alpine") + 
  geom_errorbarh(height = .1) +
  facet_grid(~ Treatment, scales = "free") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(legend.position = "none", axis.title = element_blank()) -> fig1

sheet1[21:57, ]  %>%
  select(variable, post.mean, l.95..CI, u.95..CI, pMCMC) %>%
  separate(variable, into = c("Macroregion", "Alpine", "Treatment"), sep = ":") %>%
  mutate(Alpine = gsub("Alpine", "", Alpine),
         Macroregion = gsub("Macroregion", "", Macroregion)) %>%
  rename(Mean = post.mean,
         Lower = l.95..CI,
         Upper = u.95..CI,
         p = pMCMC) -> df2

ggplot(df2, aes(y = Alpine, x = Mean, xmin = Lower, xmax = Upper, color = Alpine)) +
  geom_point() +
  labs(title = "Final germination proportion by alpine and region") + 
  geom_errorbarh(height = .1) +
  facet_grid(Macroregion ~ Treatment, scales = "free") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(legend.position = "none", axis.title = element_blank()) -> fig2
```

```{r echo = FALSE, fig.height = 1.5}
fig1
```

```{r echo = FALSE, fig.height = 3}
fig2
```

>>>>

---
title: "MCMC report"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output: pdf_document
---

@@

```{r message = FALSE, echo = FALSE, warning = FALSE}
library(tidyverse); library(here)

source(here("src", "analysis.R"))

```

# Manuscript figures

```{r echo = FALSE, fig.height = 5.5}
fig1
```

# Final germination proportions

```{r echo = FALSE, fig.height = 3}
fgFull
```

```{r echo = FALSE, fig.height = 3}
fgAlpine
```

```{r echo = FALSE, fig.height = 3}
fgRegion
```

```{r echo = FALSE, fig.height = 3}
fgDormancy
```

```{r echo = FALSE, fig.height = 3}
fgPlanttype
```
```{r echo = FALSE, fig.height = 3}
fgLifeform
```

```{r echo = FALSE, fig.height = 3}
fgLifespan
```

# Mean germination time

```{r echo = FALSE, fig.height = 3}
mgtFull
```

```{r echo = FALSE, fig.height = 3}
mgtAlpine
```

```{r echo = FALSE, fig.height = 3}
mgtRegion
```

```{r echo = FALSE, fig.height = 3}
mgtDormancy
```

```{r echo = FALSE, fig.height = 3}
mgtPlanttype
```
```{r echo = FALSE, fig.height = 3}
mgtLifeform
```

```{r echo = FALSE, fig.height = 3}
mgtLifespan
```

# Uncertainty

```{r echo = FALSE, fig.height = 3}
uncFull
```

```{r echo = FALSE, fig.height = 3}
uncAlpine
```

```{r echo = FALSE, fig.height = 3}
uncRegion
```

```{r echo = FALSE, fig.height = 3}
uncDormancy
```

```{r echo = FALSE, fig.height = 3}
uncPlanttype
```
```{r echo = FALSE, fig.height = 3}
uncLifeform
```

```{r echo = FALSE, fig.height = 3}
uncLifespan
```
